Index measures for oak decline severity using phenotypic descriptors

### 2019-12-18 manuscript/manuscript.Rmd
finished decline index discussion

- Suitability of collected phenotypic descriptors and decline indexes for describing decline status

@@

The high contribution of bleed prevalence related descriptors to the DAI is expected as this is one of the defining features of AOD [@denman2014].

There was no contribution of *A. biguttatus* exit hole occurance with with the DAI and therefore stem bleeding - smaller area surveyed compared to bleeding. It has also been found previouly that trees with bleeds do not always have exit holes as  [@brown2017a;@vansteenkiste2004].

@@

- Size differences between AOD and COD trees

The relationship of relative tree stature and the acuteness of the decline likely reflects the period of time under which these trees have been afflict. 
AOD occurs over a much shorter period compared COD and therefore has less time in which to inhibit growth of the tree as a whole.

- Refined definition of remission - repeat measurement

@@

- Crown condition descriptors most important for describing overall decline severity in the PDI.
- Bacterial bleed related descriptors are most important for describing decline acuteness.
- Decline indexes provide intuitive measures of decline severity based on simple phenotypic measurements that do not require specialist equipment

>>>>

@@

The high contribution of bleed prevalence related descriptors to the DAI is expected as this is one of the defining features of AOD [@denman2014]. 
There was no contribution of *A. biguttatus* exit hole occurance with with the DAI and therefore stem bleeding - smaller area surveyed compared to bleeding. It has also been found previouly that trees with bleeds do not always have exit holes as  [@brown2017a;@vansteenkiste2004].

@@

It was shown that tree size, reflected by the live crown ratio descriptor, contributes most to the DAI in descriminating between COD and AOD trees.
The relationship of relative tree stature and the acuteness of oak decline has not previously been shown and likely reflects the period of time under which these trees have been afflicted. 
AOD occurs over a much shorter period compared COD and therefore has less time in which to inhibit growth of the tree as a whole.

The remission trees as a group were shown to be intermediate in decline severity and type to the healthy, AOD and COD trees on both the PDI and DAI index scales.
However, this was also the most varied of the decline status groups.
It is possible that this could reflect an underly relationship of the potential for trees to recover from AOD but this is speculative and it is not possible to attribute this further with these observations.
Using these decline indexes, remission trees can be more objectively defined in terms of their temporal trajectory within the decline index continuum.

@@

- Suitability of collected phenotypic descriptors and decline indexes for describing decline status
- Crown condition descriptors most important for describing overall decline severity in the PDI.
- Bacterial bleed related descriptors are most important for describing decline acuteness.
- Decline indexes provide intuitive measures of decline severity based on simple phenotypic measurements that do not require specialist equipment
